### 2021-07-11 src/paper/data/policies.tex
Make policy data section ready for review.

Our policies usually affect one of our four contact types: households, education, work
and other contacts.
% households
For households we assume that the individuals' contacts in their households do not change
over our estimation period.
% educ models
For nurseries, preschools and schools we implement vacations as announced by the German
federal states as well as school closures, emergency care and A / B schooling where only
one half of students attends every other week or day.
% For the moment we ignore that lack of childcare leads working parents to stay home.
An approximation of the share of contacts still taking place with the different school
regulations can be found in Figure~\ref{fig:school_multiplier}.
% work
For work contacts we use the reductions in work mobility reported in the Google
Mobility Data \citep{Google2021} to calibrate our work policies. Reductions in work
contacts are not random but governed through a work contact priority where the policy
changes the threshold below which workers stay home. Figure \ref{fig:work_multiplier}
shows the share of workers that go to work over time at the federal German level. We use
the data on the state level.

In addition, for both work and school contacts we assume that hygiene measures (such as
masks, ventilation and hand washing) became more strict and more conscientiously observed
in November, leading to a reduction of 33\% in the number of contacts with the potential
to transmit Covid-19.

@@

    \caption{The Effect of School and Work Policies on the Number Contacts Taking Place}

@@

Lastly, for the other contacts category we did not calibrate them from data but estimated
the policy effects on them. Refer to Section~\ref{subsec:estimated_params} and Figure~\ref{fig:other_multiplier} in particular.

>>>>

Our policies usually affect one of our four contact types: households, education, work
and other contacts.
% households
For households we assume that the individuals' contacts in their households do not change
over our estimation period.
% educ models
For nurseries, preschools and schools we implement vacations as announced by the German
federal states as well as school closures, emergency care and rotating schooling
schedules where only one half of students attends every other week or day.% For the moment we ignore that lack of childcare leads working parents to stay home.
An approximation of the share of contacts still taking place with the different school
regulations can be found in Figure~\ref{fig:school_multiplier}.
% work
For work contacts we use the reductions in work mobility reported by the Google Mobility
Data \citep{Google2021} to calibrate our work policies. Reductions in work contacts are
not random but governed through a work contact priority where the policy changes the
threshold below which workers stay home. Figure \ref{fig:work_multiplier} shows the share
of workers that go to work over time at the federal German level. We use the data on the
state level to account for local holidays and differences in state regulations.
% hygiene umltiplier
In addition, for both work and school contacts we assume that hygiene measures (such as
masks, ventilation and hand washing) became more strict and more conscientiously observed
in November, leading to a reduction of 33\% in the number of contacts with the potential
to transmit Covid-19.

@@

    \caption{The Contact Reduction Effects of School and Work Attendance Policies}

@@

Lastly, for the other contacts category we could not calibrate the policies from data but
estimated the policy effects. The estimation and values are detailed in
Section~\ref{subsec:estimated_params} and Figure~\ref{fig:other_multiplier}.
